In the educational landscape, students often struggle with inconsistent study habits, frequently resorting to cramming before exams rather than engaging in regular, spaced learning. This approach is counterproductive as it hinders deep understanding and long-term retention of information. Many existing study tools inadvertently facilitate these poor techniques by failing to provide proper motivation to students, which undermines effective learning. 

Addressing this issue is crucial because consistent study habits enable better academic performance and reinforce essential learning skills, benefiting students both academically and personally. To combat this, we have used this project as an opportunity to create a new studying platform that promotes effective learning practices, ultimately fostering sustained habits that set students up for success. 

The platform allows teachers to create quizzes for their students to take, rewarding points based on their completion and performance. These points can be redeemed for in-app rewards such as avatars, visual themes, and titles/ranks. By capping daily point earnings, the platform encourages users to return regularly and study in bursts rather than all at once, aligning with psychological findings that small, regular study sessions promote deeper learning. 

Furthermore, the architectural focus of this project ensures scalability and a smooth development process. This approach keeps our code aligned with core functionality while ensuring its capacity to grow with an increasing number of users and content. By prioritizing architecture, the project serves as a case study demonstrating the usefulness of structural design in facilitating a seamless development journey at all stages. 

This structured approach not only addresses the problem of poor study habits but also ensures that the platform is both effective and adaptable, making it accessible to a broad audience with clear and professional language.